12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-26 rules/rules17.tex
More detailed explanation of checking for the unsat-core track

The result of a solver is considered erroneous if the response to the
\akey{check-sat} command is \texttt{sat}, or if the returned
unsatisfiable core is not well-formed (e.g., contains names of
formulas that have not been asserted before), or if the returned
unsatisfiable core is not, in fact, unsatisfiable.  The organizers
intend to check unsatisfiability by running an SMT solver on a
benchmark that asserts only those formulas in the reported core.  The
details of the checking procedure, which will be the same for all
solvers and benchmarks in the unsat-core track, are still to be
determined.

>>>>

The result of a solver is considered erroneous if the response to the
\akey{check-sat} command is \texttt{sat}, or if the returned
unsatisfiable core is not well-formed (e.g., contains names of
formulas that have not been asserted before), or if the returned
unsatisfiable core is not, in fact, unsatisfiable.

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that have been sound (i.e., not
produced any erroneous result) in the corresponding division of the
main track.  The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \textt{sat}
exceeds the number of checking solvers whose result is \textt{unsat},
or if the unsat-core producing solver is used as a checking solver and
its result is \textt{sat}.  The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.
